---
title: "Air Quality"
author: "Brandon Bevan"
date: "May 7, 2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Based from the Coursera course "Reproducible Research" by Johns Hopkins University
The goal of this document is to provide an example of "literate statistical programming" by "weaving" together English text, R Code, and graphics provided by ggplot and R's builtin plotting capabilities.

"Literate statistical programming" with R Markdown files allows for "reproducible" research through the ability of the critic to 

1. Download the markdown file

2. Re-run the analyses in R

3. Regenerate the HTML (or pdf) 

In this document, we provide a regression analysis of air quality data.


```{r}
library(datasets)
data(airquality)
summary(airquality)
```

As can be seen, the variables within the data set are Ozone levels, Solar Radiation levels, Wind, Temperature, Month, and Day measurements.

Here is a plot of each pair of variables against one another.

```{r}
pairs(airquality)
```

We will test a regression model of Ozone versus Solar Radiation.

```{r}
library(stats)
fit <- lm(Ozone ~ Solar.R, airquality)
summary(fit)
```

Next, we plot the regression line.

```{r}
y <- airquality$Solar.R 
x <- airquality$Ozone

plot(y,x)
abline(fit)
```

In conclusion, I have realized that the gap in my understanding is in interpreting measures of significance for regression lines. I am also unsure how to interpret the Mean Squared Error, whether it should be close to zero or not. Therefore, the next step in my education is learning Hypothesis Testing for regression analysis.