---
title: "Air Quality"
author: "Brandon Bevan"
date: "May 7, 2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Based from the Coursera course "Reproducible Research" by Johns Hopkins University
The goal of this document is to provide an example of "literate statistical programming" by "weaving" together English text, R Code, and graphics provided by ggplot and R's builtin plotting capabilities.

"Literate statistical programming" with R Markdown files allows for "reproducible" research through the ability of the critic to 

1. Download the markdown file

2. Re-run the analyses in R

3. Regenerate the HTML (or pdf) 

In this document, we provide a regression analysis of air quality data.


```{r}
library(datasets)
data(airquality)
summary(airquality)
```

As can be seen, the variables within the data set are Ozone levels, Solar Radiation levels, Wind, Temperature, Month, and Day measurements.

Here is a plot of each pair of variables against one another.

```{r}
pairs(airquality)
```

We will test a regression model of Ozone versus Temperature.

```{r}
library(stats)
fit <- lm(Ozone ~ Temp, airquality)
summary(fit)
```

Next, we plot the regression line.

```{r}
x <- airquality$Temp 
y <- airquality$Ozone

plot(x,y)
abline(fit)
```

We can see that temperature may be a good predictor for Ozone levels, leading us to believe that increasing temperatures may positively correlate to increasing Ozone levels.